Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-03-23 referee_process/first_submission/referee_response.tex

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Editor,
$\,$\newline

\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}

\begin{singlespace}
We thank the two referees for their careful reading of our letter
and their detailed and constructive critique.
In responding to these two reports, the science within
our paper has been significantly strengthened.
Addressing the questions raised by report A has led us to undertake
our first 3D runs, and we report on the results of these in the
revised draft.  In responding to report B,
we realized that our previous definition of the
Nusselt number (Nu) was flawed, and have since defined
a slightly modified, more appropriate Nu.  This new definition better unifies
the results at low and high Mach number (Ma) and makes it easier to understand
the changes between the low and high Ma regimes. We have streamlined our discussion
of the control parameters and have shown how evolved properties (e.g, Ma) depend
on the control parameters of our experiment.  Our previous presentation of the
experiment was confusing, and following the report's comments we feel that we
have improved the presentation.

@@

We apologize for the three month delay between receiving the referee reports
and the return of the revised draft.  In these months we have
recomputed all solutions, designed and tested our 3D implementation, and
thought carefully about the proper definition of Nu.  Through this
process we have gained a greater understanding of the fundamental
fluid properties in our simulations.

We include the revised version of our paper, ``Convective heat transport in stratified
atmospheres at low and high Mach number,'' in which we have addressed the critique contained
in both reports.  We think the science has been substantially improved by the critique, as has
the presentation of the experiment and the results.  The text and figures have been significantly
revised in addressing the critique.  
Below we include a detailed response to the reports; we include the text of
the reports in their entirety along with our responses inline.  We address major
points of the critiques first and then address minor points.

@@

$\,$\newline
\noindent
Sincerely,

Evan H. Anders \& Benjamin P. Brown

%\end{singlespace}

$\,$
\newline
$\,$
\newline
\noindent
\Large{\textbf{Response to report A:}}\newline$\,$\newline\indent
\large{\textbf{Major Points}}

@@

We now have run and analyzed select 3D cases at both low and high $\epsilon$
at select values of the Rayleigh number.  These simulations have shown
us that many fluid properties (e.g., the density profile, Mach number, and Reynolds number)
of the evolved 3D state are similar to the 2D simulations.  We now report on these
limited 3D results as well as our more extensive 2D results. These results are shown
in Figs. 1, 3, and 4, with large symbols, and are discussed in the text.
Broadly, there seems to be some agreement between the 2D and 3D dynamics.

\begin{myquotation}
The Letter is clearly written with a well balanced general
introduction to the field, a formulation of particular simplifications
of basic equations of motion and a presentation of the results of
numerical simulations. According to my understanding, the paper should
be interesting for non-experts in the field. I tend to recommend this
manuscript for publication in PRL, after detailed clarification of the
relations between two- and three-dimensional description on the basics
of Rayleigh-Bernard convection and on their generalization to the
compressible case.
\end{myquotation}

This concludes our response to report A.  We thank referee A for this report.

$\,$
\newline
$\,$
\newline
\noindent
\Large{\textbf{Response to report B:}}\newline$\,$\newline\indent
\large{\textbf{Major Points}}

@@

\begin{myquotation}
...However, it is true that the
interesting change in transport results appear when the flow becomes
supersonic, but this could mean high superadiabaticity (epsilon) *or*
high Ra (for fixed Pr). The results should all really be cast as
`at high enough Ra or high enough superadiabaticity, a high Ma flow
results and this changes the transport characteristics'.
Ultimately, the scaling results exhibited are in terms of Ra, and this
makes perfect sense, although these results are only confined to a
small paragraph at the end of the results section without much
elaboration or explanation. I personally would like a much more causal
relationship explained between the shock heating and `spinners'
and the heat transport results.
\end{myquotation}
In revisiting our results, we found that the substantial differences between
low and high $\epsilon$ in heat transport arose from a poor definition of
Nu and from changes to the overall stratification.  We have determined a
more consistent version of Nu (based on current properties rather than initial
properties).  Now, high and low $\epsilon$ transport is substantially similar.
We do see a small change in transport when 2D simulations achieve a mean
Ma of O(1), and to test this we have conducted an additional suite of
experiments at higher $\epsilon = 1$.  In these solutions, all of the flow
properties show a change of behavior at the point at which the flows enter the
sonic regime.  This is shown in Figs. 1, 3, and 4 and discussed in the text.

Figure 4 shows a surprising result.  We have removed the former Fig. 3 (fluxes
as a function of height) so that we can discuss the result in our current
Fig. 4 fully.  We find that the density contrast across the domain at high $\epsilon$
appreciably shrinks in the evolved state compared to the initial state.  Furthermore, we find
that density inversions form near the boundary layers of these atmospheres once the mean atmospheric Mach number approaches
one, and show that this density inversion becomes significant at high Ra and high $\epsilon$,
and persists in 3D.  This is discussed fully in the Results \& Discussion section.

@@

We have addressed the major points in the critique; we now continue with the
minor points and clarifications.

$\,$
\newline
$\,$
\newline
\indent
\large{\textbf{Minor Points}}\newline
\begin{myquotation}
Beyond this main issue, there are a lot of small things that I don't
understand, which I will try and list here, in chronological order.

`Numerical constraints ... to moderately high Ma': What is the
numerical constraint of low Ma flow?
\end{myquotation}
When the convection is low Ma, the convective dynamics are much slower
than the linear acoustic waves.  In explicit timestepping schemes, these
fast acoustic waves set the Courant Friedrich Lewy (CFL) limit.
By employing modern IMEX schemes, we are able to implicitly involve these
fast linear waves and timestep on the timescale of the slow convective
dynamics.    This is detailed in the second to
last paragraph of the Experiment section.

\begin{myquotation}
`RB' By `Rayleigh-Benard problem' here I assume that the
authors are referring to Boussinesq dynamics? It might be a good idea
to make this clear.
\end{myquotation}
We have clarified that we are referring to incompressible Boussinesq convection
in the Introduction.

\begin{myquotation}
`the Ma is controlled by the superadiabatic excess': It is clear
from Fig 1 that this is not a complete statement.
\end{myquotation}
We have clarified the discussion of how Ma scales with $\epsilon$ and
Ra throughout the text.

@@

\begin{myquotation}
Experiment

Eqn (1): Better define co-ordinates, especially $z$ and $z_0$
\end{myquotation}
We agree that $z_0$ was confusing notation and this has been removed.  
We define $z$ shortly below Eqn (1).

\begin{myquotation}
The non-dimensionalization is very confusingly written. Can you write
out the non-dimensionalised polytope? This section also says that the
`timescale is the isothermal sound crossing time of the layer'
and then two sentences later says that `we use buoyancy time
units', so which is it? The definition of the latter does look like
the sqrt(epsilon) so maybe these are the same?
\end{myquotation}
We have clarified that the equations are non-dimensionalized on
the isothermal sound crossing timescale.  We have also clarified
how the evolution time of the flow is linked to the buoyancy time.
This appears in the final paragraph of the experiment section.

\begin{myquotation}
`The scaling of the entropy gradient with epsilon ... evolved
values ': I really have no idea what these two sentences mean,
sorry!
\end{myquotation}
We agree that this sentence was confusing and have moved the
discussion of the magnitude of evolved fluctuations to the
discussion of Fig. 1.

\begin{myquotation}
Eqns: I don't understand why these equations are formulated with
gradients of nu when mu is constant. The stress tensor only depends on
mu and so this can be pulled out of all derivatives. Or am I missing
something? The case of constant nu and therefore variable mu is much
harder. Similarly for the formulation in terms of chi and not the
thermal conductivity; variable thermal conductivity is hard but
variable chi is easy. Why not write in terms of mu and k not nu and
chi?
\end{myquotation}
Our equations are formulated as the evolution of velocities rather
than momentum, and in this formulation $\nu$ and $\chi$ are the
natural variables.  If $\nu$ and $\chi$ are constant in space,
the problem becomes a constant coefficient problem and is numerically
simple.  However, a spatially constant $\nu$ and $\chi$ does not satisfy
thermal equilibrium within the initial polytrope, which is only satisfied when
$\kappa = \rho\chi$ is constant.  To satisfy thermal equilibrium required
a gradient in $\chi$, and to satisfy a constant Pr through the domain we
must also have a gradient in $\nu$.  $\nu$ and $\chi$ are now nonconstant
coefficients, and this approach, as we take here, is much more challenging numerically. 
 We have
clarified and detailed the profiles of $\nu, \chi, \mu, \text{and} \kappa$
in the second paragraph of the experiment section.

\begin{myquotation}
`IMEX': I am assuming this acronym stands for implicit-explicit?
Maybe write out?
\end{myquotation}
We have spelled this out in the second to last paragraph of the Experiment section.

\begin{myquotation}
`extended to include variable nu and chi' : see above. This seems
very unnecessary!

@@

Results

$d_z T_{ad} = 0$: This is only true for liquids not gases. See Speigel and
Veronis 1960.
\end{myquotation}
This is a good point that we had not appreciated.  Most of the studies of Boussinesq
convection with which we are familiar make the assumption that the fluid is incompressible.
It is true that in an ideal gas which is compressible but barely stratified, the
adiabatic temperature gradient is what we found and what is reported by
Spiegel and Veronis, $\partial_z T_{ad} = -g/c_P$, \cite{spiegel&veronis1960}.
We have updated the text following Eqn 8 to reflect this.

\begin{myquotation}
`While it has been suggested that pressure forces...': I do not
understand the discussion here. Do the authors regard the breakup of
the down flows as an extreme version of asymmetry?
\end{myquotation}
Being unable to determine how $\epsilon$ affects symmetries in the
flow, we have removed this discussion.

@@

\begin{myquotation}
`exhibit states in which the flux entering...': Surely in a
stationary state the flux in has to equal the flux out. Are the
authors saying that this is not a stationary state?
\end{myquotation}
As detailed in the revised text, the combination of fixed-temperature
boundary conditions and no-slip boundary conditions allows the system to alternate between
roll states of convection and shear states of convection.  These states persist over long
time scales (hundreds of buoyancy times) and the atmosphere is in flux disequilibrium in both states.
A sensible equilibrium and average emerges over long times.  This discussion appears with
the discussion of Fig. 3a.

\begin{myquotation}
Discussion

Can the authors demonstrate the basic principles of whatever balance
is described by the Grossman-Lohse theory?
\end{myquotation}
We believe that the Grossman-Lohse theory, which models the energy dissipation rate of both
kinetic and potential energies, could be extended to stratified, compressible flows which also
have potential energy.  At low $\epsilon$, it seems the extension would be easier to
develop. However, we are inexperienced in boundary layer theory and presently 
cannot say with certainty that an expansion of this theory to stratified convection is tractable. 
We have removed this suggestion from letter.  We have also combined the Results \& Discussion
sections.

### 2017-03-23 tex/nusselt_paper.tex
near-final versions uploaded

\begin{abstract}
Convection in astrophysical systems is stratified and
often occurs at high Rayleigh number (Ra) and low
Mach number (Ma).
Here we study stratified convection in the context of 
plane-parallel, polytropically stratified atmospheres. 
We perform a suite of 2D and 3D simulations in which we vary the initial
superadiabaticity ($\epsilon$) and Ra at a set
initial density stratification ($n_{\rho}$), aspect
ratio, and Prandtl number (Pr).
We find that Ma is a strong function of $\epsilon$
in both 2D and 3D simulations, and that it is a 
weak function of Ra in 2D.
The scaling of evolved fluid properties (Nusselt number, Reynolds number,
stratification) differs in the subsonic and supersonic regimes; however,
aside from the sonic transition, the evolved flow properties
of low and high Ma flows are nearly identical.  Our limited 3D runs suggest that
evolved fluid properties behave similarly in 2D and 3D, but with modified
scaling laws.
\end{abstract}
\maketitle

@@

In this letter we study the behavior of convective heat transport, 
quantified by the Nusselt number (Nu), in plane-parallel, 
two- and three-dimensional, polytropically stratified atmospheres.  
We vary $\epsilon$ and Ra while holding Pr, aspect ratio, boundary conditions,
and initial atmospheric stratification
constant.  We also examine the behavior of flow properties, as quantifed by Ma and Re.

@@

%
%We examine the simplest stratified extension of RB by studying a
%fluid composed of monatomic ideal gas particles with an adiabatic 
%index of $\gamma = 5/3$ and whose equation of state is $P = R\rho T$. 
%This is consistent with the approach used in earlier work.
%The initial atmosphere is a plane-parallel polytrope in which 
%the gravitational acceleration and conductive flux, 
%$\bm{F}_{\text{cond,0}} = -\kappa \partial_z T_0$, do not vary with depth. To
%achieve the latter condition, both $\kappa$ and $\partial_z T_0$ are constant.
%Under these assumptions, satisfying hydrostatic 
%equilibrium produces a stratification of
%\begin{equation}
%\begin{split}
%\rho_0(z) &= \rho_{t}(z_0 - z)^m, \\
%T_0(z)    &= T_{t}(z_0 - z),
%\label{eqn:polytrope}
%\end{split}
%\end{equation}
%where $m = m_{\text{ad}} - \epsilon$ is the polytropic index.
%The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$, and
%the superadiabatic excess is $\epsilon$ which sets the scale 
%of the entropy gradient ($\partial_z S_0 \propto -\epsilon$).
%A significant advance of this work is the ability to study large 
%and small values of $\epsilon$, as will be discussed.
%Thermodynamic variables are nondimensionalized at the 
%top of the atmosphere as  $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, 
%requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
%By this choice, the non-dimensional length scale is the inverse 
%temperature gradient scale and the timescale is the isothermal 
%sound crossing time of this unit length.
%The height $z$ increases upwards within $[0, L_{z}]$, 
%where $L_{z} = e^{n_{\rho}/m} - 1$ is
%determined by $n_\rho$ and $\epsilon$.
%The characteristic timescale of convective dynamics
%is related to the atmospheric buoyancy time, 
%$t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
%Throughout this letter, we use buoyancy time units and 
%choose $n_{\rho} = 3$ such that the 
%initial density varies by a factor of 20.
%All atmospheres studied here have an aspect ratio of 4, 
%such that $L_x = 4L_z$.
%

@@

We impose impenetrable, stress free, fixed temperature boundary conditions at
the top and bottom of the domain such that 
$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. 
$T_1$ is initially filled with
random white noise whose magnitude is infinitesimal
compared to $T_0$ and $\epsilon$.
We filter this noise spectrum in coefficient space, 
such that only the lower 25\% of the coefficients
have power. We non-dimensionalize our computational domains by setting
all thermodynamic variables to unity at $z = L_z$ choosing
$R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
length scale is the inverse temperature gradient scale and the 
timescale is the isothermal sound crossing time, 
$\tau_I$, of this unit length.
Meaningful convective dynamics occur on 
timescales of the atmospheric buoyancy time,
$t_b = \tau_I \sqrt{L_z/g\epsilon}$. 
All reported results are taken from time averages
over many $t_b$ beginning \{100, 40\}$t_b$
after the start of our \{2D, 3D\} simulations in order to
assure our results are not biased by the convective transient.

@@

We measure the adiabatic Mach number (Ma = $|\bm{u}|/\sqrt{\gamma T}$).
We find that Ma is a strong function of 
$\epsilon$ and a weak function of Ra.  
In our 2D runs, when Ma $< 1$ we observe a scaling law of
Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$.
this relation breaks down as the mean
Ma approaches 1 (see Fig. \ref{fig:ma_v_eps}).  This transition
occurs near Ra/Ra$_\text{crit} \approx \{10^{2}, 10^{3}\}$ for $\epsilon = \{1, 0.5\}$.
In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
Ma $\propto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
The value of $\epsilon$ also sets the size of the
evolved thermodynamic fluctuations, such that
$T_1/T_0 \propto \epsilon$ and $\rho_1/\rho_0 \propto \epsilon$.  
These fluctuations are very small when $\epsilon$ and Ma are small,
but can be O(1) for values of $\epsilon$ near 1.

@@

Low Ma flows (e.g., $\epsilon = 10^{-4}$)
display the classic narrow downflow and broad upflow lanes of stratified
convection (Fig. \ref{fig:entropy_snapshots}a).
At high Ma (e.g., $\epsilon = 0.5$), bulk thermodynamic structures are similar but
shock systems form in the upper atmosphere near downflow lanes 
for sufficiently large values of $\epsilon$ and Ra (Fig. \ref{fig:entropy_snapshots}b,c).
Similar shock phenomena were reported in
both two \cite{cattaneo&all1990} and 
three \cite{malagoli&all1990} dimensional polytropic simulations previously.
As Ra is increased to large values 
(Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
no longer span the whole domain but rather break up into 
small eddies which traverse the domain multiple
times before diffusing.  Our choice of fixed-temperature, stress free boundary conditions 
allows the flux at the boundaries to vary, while also allowing
for mean horizontal velocity profiles along the boundaries (winds).
We find these windy convective states, reminiscent of similar states
in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ for high
values of Ra. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
transport alternate with windy states of lower transport.

@@

We have observed interesting phenomena, such as time-dependent oscillating shearing windy
states in our 2D simulations.  Unlike in RB \cite{goluskin&all2014}, our solutions with
windy states have transport which scales in line with our non-windy solutions.
Furthermore, the stratification of 
these polytropic atmospheres evolves in a complex
manner.  Future work should aim to 
understand the importance of stratification on
convective heat transport and other flow properties.

Our studies
here will serve as a foundation both for understanding and 
comparing heat transport in stratified convection
to that in RB convection \cite{johnston&doering2009}, 
and for future studies of transport in stratified convection.  
These results can be used to determine if simplified equation sets, 
such as the anelastic equations, carry heat in the same manner as the 
FC equations.
This work will also be useful in coming to understand more realistic systems, 
such as rapidly rotating atmospheres \cite{julien&all2012},
atmospheres bounded by stable regions \cite{hurlburt&all1986}, 
or regions with realistic profiles of $\kappa$.

>>>>

\begin{abstract}
%Convection in astrophysical systems is stratified and
%often occurs at high Rayleigh number (Ra) and low
%Mach number (Ma).
We study stratified convection in the context of 
plane-parallel, polytropically stratified atmospheres. 
We perform a suite of 2D and 3D simulations in which we vary the initial
superadiabaticity ($\epsilon$) and the Rayleigh number (Ra) at a set
initial density stratification, aspect
ratio, and Prandtl number.
We find that the Mach number (Ma) is a strong function of $\epsilon$
in both 2D and 3D simulations, and that it is a 
weak function of Ra in 2D.
Surprisingly, we find that the evolved heat transport, 
quantified by the Nusselt number (Nu),
follows scaling relationships similar to those found in the well-studied, 
incompressble Rayleigh-B\'{e}nard problem.
The scaling of evolved fluid properties (Nu, Reynolds number,
stratification) differs in the subsonic and supersonic regimes; 
aside from the sonic transition, the evolved flow properties
of low and high Ma flows are nearly identical.  
Our limited 3D runs suggest that
evolved fluid properties behave similarly in 2D and 3D.
\end{abstract}
\maketitle

@@

In this letter we study the behavior of convective heat transport, 
quantified by the Nusselt number (Nu), in plane-parallel, 
two- and three-dimensional, polytropically stratified atmospheres.  
We vary $\epsilon$ and Ra while holding Pr, aspect ratio, boundary conditions,
and initial atmospheric stratification
constant.  We also examine the behavior of flow properties, as quantified by Ma and Re.

@@

@@

We impose impenetrable, stress free, fixed temperature boundary conditions at
the top and bottom of the domain such that 
$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. 
$T_1$ is initially filled with
random white noise whose magnitude is infinitesimal
compared to $T_0$ and $\epsilon$.
We filter this noise spectrum in coefficient space, 
such that only the lower 25\% of the coefficients
have power. We nondimensionalize our computational domains by setting
all thermodynamic variables to unity at $z = L_z$ choosing
$R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
length scale is the inverse temperature gradient scale and the 
timescale is the isothermal sound crossing time, 
$\tau_I$, of this unit length.
Meaningful convective dynamics occur on 
timescales of the atmospheric buoyancy time,
$t_b = \tau_I \sqrt{L_z/g\epsilon}$. 
All reported results are taken from time averages
over many $t_b$ beginning \{100, 40\}$t_b$
after the start of our \{2D, 3D\} simulations in order to
assure our results are not biased by the convective transient.

@@

We measure the adiabatic Mach number (Ma = $|\bm{u}|/\sqrt{\gamma T}$).
We find that Ma is a strong function of 
$\epsilon$ and a weak function of Ra.  
In our 2D runs, when Ma $< 1$ we observe a scaling law of
Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$.
This relation breaks down as the mean
Ma approaches 1 (see Fig. \ref{fig:ma_v_eps}).  This transition
occurs near Ra/Ra$_\text{crit} \approx \{10^{2}, 10^{3}\}$ for $\epsilon = \{1, 0.5\}$.
In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
Ma $\propto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
The value of $\epsilon$ also sets the size of the
evolved thermodynamic fluctuations, such that
$T_1/T_0 \propto \epsilon$ and $\rho_1/\rho_0 \propto \epsilon$.  
These fluctuations are very small when $\epsilon$ and Ma are small,
but can be O(1) for values of $\epsilon$ near 1.

@@

Low Ma flows (e.g., $\epsilon = 10^{-4}$)
display the classic narrow downflow and broad upflow lanes of stratified
convection (Fig. \ref{fig:entropy_snapshots}a).
At high Ma (e.g., $\epsilon = 0.5$, Ra/Ra$_{\text{crit}} \gtrsim 10^3$), 
bulk thermodynamic structures are similar but
shock systems form in the upper atmosphere near downflow lanes 
(Fig. \ref{fig:entropy_snapshots}b\&c).
These shock phenomena were reported in
two \cite{cattaneo&all1990} and 
three \cite{malagoli&all1990} dimensional polytropic simulations previously.
As Ra is increased to large values 
(Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
no longer span the domain depth; rather, they break up into 
small eddies which traverse the domain multiple
times before diffusing.  Our choice of fixed-temperature, stress free boundary conditions 
allows the flux at the boundaries to vary, while also allowing
for mean horizontal velocity profiles along the boundaries (winds).
We find these windy convective states, reminiscent of similar states
in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ and
Ra/Ra$_{\text{crit}} \gtrsim 10^{3}$. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
transport alternate with windy states of lower transport.

@@

We observe interesting phenomena, such as time-dependent, windy
states of shear in our 2D simulations.  
Unlike in RB \cite{goluskin&all2014}, our solutions with
windy states have transport which scales in line with our non-windy solutions.
Furthermore, the stratification of 
these polytropic atmospheres evolves in a complex
manner.  Future work should aim to 
understand the importance of stratification on
convective heat transport and other flow properties.

Our studies here will serve as a foundation for 
comparing heat transport in stratified convection
to that in RB convection \cite{johnston&doering2009}
and for better quantifying transport in stratified convection.  
These results can be used to determine if fluid properties
scale appropriately in simplified equation sets, 
such as the anelastic equations.
This work will also be useful in coming to understand more realistic systems, 
such as rapidly rotating atmospheres \cite{julien&all2012},
atmospheres bounded by stable regions \cite{hurlburt&all1986}, 
and regions with realistic profiles of $\kappa$.
